\section{Topology Comparison}
As previously noted, a high-voltage DC-DC step-up stage is essential to power the ion thruster's acceleration grids. While several methods exist to achieve this, standard modified boost topologies—such as the Flyback or Ćuk converter—are frequently utilized \cite{mohan2003power}. However, these topologies are typically constrained by a practical voltage gain limit, often restricted to a factor of 1 to 10 times the input voltage \cite{tofoli2015survey}. Ion thrusters require beam voltages on the order of 1000V, necessitating a step-up ratio of 10 to 50 times the typical spacecraft bus voltage. Consequently, achieving such high transformation ratios requires either a multi-stage conversion architecture or inverter based topologies. In the latter, the DC input is first inverted into a high-frequency AC signal. In an isolated topology, this AC intermediate is then stepped up through a high-turns-ratio transformer and rectified back to DC, providing both the necessary voltage gain and galvanic isolation \cite{mohan2003power}. An alternative approach is to use a non-isolated topology, by increasing the high frequency voltage with a parallel resonant circuit, before rectifying it back to DC.
\subsection{Hard Switching}
This architecture is typically implemented using a full-bridge inverter to modulate the DC input into a high-frequency AC signal. By commutating the bridge transistors in a specific switching sequence, a Pulse-Width Modulated (PWM) waveform is generated. However, because semiconductor switches are non-ideal, they undergo finite transition periods. During these "turn-on" and "turn-off" intervals, the simultaneous presence of non-zero voltage across the switch and current through it results in a V-I overlap, leading to significant instantaneous power dissipation. During the turn-off transition, parasitic inductances in the circuit path prevent an instantaneous collapse of current, inducing voltage spikes and prolonging the overlap. Conversely, the turn-on transition is further penalized by the reverse recovery current of the anti-parallel diodes. This phenomenon forces a transient current spike that exceeds the steady-state load current, further exacerbating switching losses \cite{kassakian2023principles}.
\subsection{Soft Switching: Resonant Converters}
% explain briefly what soft switching is and how it differs from hard switching, then introduce resonant converters as a common implementation of soft switching citing the mohan textbook and other relevant sources. 
Soft switching describes a technique where the power semiconductor devices in a converter are switched on or off during a time frame, where either the voltage across the device or the current through it is already zero~\cite{mohan2003power}. While the former is known as Zero Voltage Switching (ZVS), the latter is referred to as Zero Current Switching (ZCS) and both methods aim to minimize switching losses and can provide additional benefits such as reduced electromagnetic interference (EMI) due to lower $dv/dt$ and $di/dt$ rates as typically encountered with hard-switched techniques~\cite{bellar1998review}. Both techniques archieve this, by reducing or even eliminating the overlapping area of the voltage and current waveforms during switching transitions~\cite{Chengetal2021}. The implementation of ZCS and ZVS can be archieved by making use of the frequency dependent behavior of a resonant circuit~\cite{mohan2003power}. Since for ion thruster applications, the goal is to step up the voltage, the resonant circuit typically consists of a parallel capacitance and a series inductance. At the resonant frequency, the reactances of the inductor and capacitor cancel and the network behaves as a purely resistive load. Below the resonant frequency, the network behaves inductively and above capacitively. This behavior can be exploited to shape the voltage and current waveforms to achieve ZVS or ZCS~\cite{mohan2003power}. While various approaches to archieve ZVS or ZCS exist~\cite{Chengetal2021}, in the following the general principle for resonant converters is explained.
\subsubsection{Zero Current Switching}
For ZCS, the switching frequency is set slightly above the resonant frequency, which results in a slightly capacitive load, making the current lead the voltage. This allows the current through the switch to cross zero before the voltage transitions, thus creating a window for the switch to turn off without any current flowing through it and effectively mitigating switch-off losses~\cite{mohan2003power}. During this window the now negative current flows through the anti-parallel diode of the switch, until the negative switch pair of the converter turn on. Note that for resonant ZCS on its own, this switch-turn on transition is still hard-switched and thus ZCS on its own only mitigates switch-off losses~\cite{mohan2003power}.
\subsubsection{Zero Voltage Switching}
ZVS on the other hand, is achieved by setting the switching frequency slightly below the resonant frequency, which results in a slightly inductive load, making the voltage lead the current. This allows the voltage across the switch to cross zero before the current transitions, creating a window for the switch to turn on without any voltage across it and thus eliminating switch-on losses~\cite{mohan2003power}. A significant implication of this is, that with ZVS also the reverse recovery losses of the anti-parallel diode are mitigated. On its own ZVS only mitigates switch-on losses, but by adding small parallel capacitances to the switches, which for power MOSFETs are are already present as output capacitances, through a delay of the gate signals, a short commutation window can be created, where all four transistors are off, allowing also for soft turn-off switching~\cite{mohan2003power}.

\subsection{Efficiency Comparison}
%Introductory sentence about the importance of efficiency in ion thruster applications 
For space applications, such as ion thrusters, efficiency is a critical parameter as it directly impacts the specific power...
%then cite following paper from cheng
In high voltage non-isolated DC to DC converters with high switching frequencies, switching losses, are generally considered the dominant loss mechanism~\cite{Chengetal2021}. Hence making use of the mentioned soft switching techniques, greatly improves the efficiency of the converters. State-of-the-art non-isolated soft-switching DC-DC converters have been reported to achieve efficiencies up to 98\% with control only technologies (COT)~\cite{Chengetal2021}, without the use of complex multi-level topologies or additional circuitry, other than the present resonant network. By using passive snubber circuits, even efficiencies up to 99\% have been reached~\cite{Chengetal2021}, although resulting in higher circuit complexity. For ion thruster applications, where high voltages, but relatively low currents are required, COT soft-switching converters are particularly promising as they can archieve this without adding drastically to system complexity~\cite{Chengetal2021}.
\subsection{Weight Comparison}
The mass of ion thruster power conversion units is a critical constraint in space applications, where payload weight directly dictates launch costs and mission feasibility. Hard-switching architectures necessitate heavy external dv/dt filters to suppress voltage spikes and protect sensitive components. As noted by Cai et al. \cite{cai2019voltage}, these passive filters significantly increase the overall size and weight of the propulsion system. While soft-switching can reduce total mass by integrating the filtering effect into the switching transition, research into weight optimization through the control of these transitions remains limited.

\subsection{Reliability Comparison}
The reliability of power conversion for ion thrusters involves a trade-off between electrical stress and architectural complexity. Tang et al. \cite{tang1998emi} demonstrate that soft-switching improves reliability by reducing $dv/dt$ and $di/dt$ rates, which lowers electromagnetic interference (EMI) and common-mode noise compared to hard-switching. In the context of space propulsion, this reduction is critical as high EMI can interfere with sensitive spacecraft antennas and communication links. By using snubber capacitors to slow voltage transitions, soft-switching mitigates stress on insulation and parasitic components within the thruster's power processing unit. However, this is offset by a higher component count, including auxiliary switches and resonant inductors, which statistically increases potential failure points. % include paper on hard and soft switch to show the diff in component count
Furthermore, the increased system complexity required for precise timing control adds vulnerability; any control failure can lead to hard-switching under high-stress conditions, potentially negating the reliability benefits for long-duration missions.