\section{Introduction}
%% Giorgio
Ion thrusters have become the primary propulsion choice for long-duration space missions, ranging from satellite station-keeping to deep-space exploration, due to their high specific impulse \cite{Mazouffre2016}. These systems generate thrust by ionizing a propellant and accelerating it through electromagnetic or electrostatic fields. A critical intermediary in this process is the Power Processing Unit (PPU), which utilizes DC-DC converters to bridge the gap between low-voltage solar arrays and high-voltage thruster requirements.

DC-DC converters are essential for stepping up bus voltages (typically 28V to 100V) to the kilovolt levels necessary for beam acceleration \cite{Faircloth2026}. They also provide precise regulation for independent power rails, including discharge, heater, and neutralizer supplies. Beyond voltage transformation, these converters ensure system reliability by providing galvanic isolation and rapid fault protection against plasma arcing. Consequently, converter design is a fundamental determinant of PPU efficiency and mass.



%% Paul
% Hard Switched DC-DC Converters: What they are, why they were used, and what are their problems regarding switching losses and EMI.
% Softswitched DC-DC Converters: What they are, how they work, and their advantages in terms of reduced switching losses and EMI. But they come with increased complexity and therefore weight, which is crucial in satellite applications.
% Something like this (gemini): 
For the DC-DC converter different topologies exist, which can be broadly categorized into hard-switched and soft-switched (resonant) converters. 
The primary motivation for investigating resonant converter topologies in ion propulsion is the relationship between switching frequency and converter system mass. In traditional power electronic circuits, using hard-switched devices, switching losses are directly proportional to the operating frequency. While increasing frequency is the standard method for reducing the size of magnetic components like inductors, and therefore their weight, it leads to power dissipation in hard-switched systems where voltage and current overlap during transitions. Theoretical research~\cite{bellar1998review}, suggests that by integrating a resonant network, the converter can achieve Zero Voltage Switching (ZVS) or Zero Current Switching (ZCS). This effectively shapes the switching waveforms so that transitions occur only when the voltage or current is zero, hence the power dissipated during switching is minimized. The key advantage is hence, decoupling efficiency from frequency. This is especially relevant for converters for satellite applications, such as ion thrusters, where the core engineering challenge is maximizing the effective specific power ($kW/kg$) of components~\cite{gao2017soft}. On the other hand, soft-switched converters need additional circuitry to achieve ZVS or ZCS, which increases the overall system complexity and mass. 

Additionally, current trends focus on wide-bandgap switches and miniaturization to increase power density \cite{Comparini2012}. However, a knowledge gap remains regarding the comparative performance of these topologies under space constraints. This review evaluates both architectures to identify the optimal design for modern ion thruster PPUs.